A {practical} review on linear and nonlinear global approaches to stability analysis

### 2018-06-04 ARTICLE_STABFEM/ARTICLE_ASME_V2.tex
D39: End of the Day: David, can you read what I have done ???

In the nonlinear r{\color{red}e}gime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
Instead, {\color{red} we taken the decomposition ${\bf q}={\bf q}_m({\bf x})+{\bf q}'({\bf x},t)$, with ${\bf q}'$ the nonlinear perturbation and ${\bf q}_m$ the {\em mean flow} defined as the time-average  of the flow:}
\be{defumean}
{\bf q}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf q}({\bf x},t)  dt,
\ee
where $T = 2\pi/\omega$  is the period of the oscillation cycle.

@@

{\color{red} Finally, the associated Drag and Lift are given respectively by:
\be{drag_cos}
\begin{aligned}
F_{x,WNL} = F_{x}({\bf q}_{bc})&+\epsilon^2 \big( 
F_{x}({\bf q}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}).{\bf n}_x \big)\\
&+|A|^2 F_{x}({\bf q}_{2,0})\\
&+2|A|^2\big(F_{x,r}({\bf q}_{2,2})\cos(2\omega t)
-F_{x,i}({\bf q}_{2,2})\sin(2\omega t) \big),
\end{aligned}
\ee
\be{lift_cos}
\begin{aligned}
F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{q}})\cos(\omega t)-
|A|_i F_{x,i}({\bf \hat{q}})\sin(\omega t) \big),\\
\end{aligned}
\ee
where $F_{x}$ and $F_{y}$ are given by \ref{drag} and \ref{lift}, respectively. All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 3 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ the fourth and fifth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ the first and second terms of \ref{lift_cos}. We note that the \textit{sine} term is associated to the phase of the forces in a physical way. }

@@

{\color{red} 
The forces coefficients given by $F_x({\bf q})$ and $F_y({\bf q})$ are then converted in the more traditional form, $C_x=2F_x({\bf q})$ and $C_y=2F_y({\bf q})$.
}
As can be seen on figure \ref{fig:Comp2},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.? and also observed by Tchoufag et al. \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results). {\color{red} These aspects are justified by the pertubative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.  }

>>>>

In the nonlinear r{\color{red}e}gime, the {\em base flow} introduced in the linear theory is not directly accessible and no longer relevant, especially when the oscillation amplitudes become large. 
Instead, {\color{red} we taken the Reynolds decomposition ${\bf q}={\bf q}_m({\bf x})+{\bf q}'({\bf x},t)$, with ${\bf q}'$ the nonlinear perturbation and ${\bf q}_m$ the {\em mean flow} defined as the time-average  of the flow:}
\be{defumean}
{\bf q}_m({\bf x})  = \frac{1}{T} \int_0^{T}  {\bf q}({\bf x},t)  dt,
\ee
where $T = 2\pi/\omega$  is the period of the oscillation cycle.

@@

{\color{red} Finally, the associated Drag and Lift are given respectively by:
\be{drag_cos}
\begin{aligned}
F_{x,WNL} = F_{x}({\bf q}_{bc})&+\epsilon^2 \big( 
F_{x}({\bf q}_{\epsilon})- 2\mathsf{D}({\bf u}_{bc}).{\bf n}_x \big)\\
&+|A|^2 F_{x}({\bf q}_{2,0})\\
&+2|A|^2\big(F_{x,r}({\bf q}_{2,2})\cos(2\omega t)
-F_{x,i}({\bf q}_{2,2})\sin(2\omega t) \big),
\end{aligned}
\ee
\be{lift_cos}
\begin{aligned}
F_{y,WNL} =2\big(|A|_r F_{x,r}({\bf \hat{q}})\cos(\omega t)-
|A|_i F_{x,i}({\bf \hat{q}})\sin(\omega t) \big),\\
\end{aligned}
\ee
where $F_{x}$ and $F_{y}$ are given by \ref{drag} and \ref{lift}, respectively. All terms in these equations can be matched with the interesting ones in \ref{drag_lift_def}: $F_{x,0}$ is the first 4 terms of \ref{drag_cos}; $F_{x,2,c}$, $F_{x,2,s}$ are the fifth and sixth terms of \ref{drag_cos}; $F_{y,1,c}$, $F_{y,1,s}$ are the first and second terms of \ref{lift_cos}. We note that the \textit{sine} term is associated to the phase of the forces in a physical way. }

@@

{\color{red} 
The forces coefficients given by $F_x({\bf q})$ and $F_y({\bf q})$ are then converted in a more traditional form, $C_x=2F_x({\bf q})$ and $C_y=2F_y({\bf q})$.
}
As can be seen on figure \ref{fig:Comp2},  the approach gives good prediction in the immediate vicinity of $Re_c$, but deviation appears very rapidly and disagreement is already large at $Re=48$ (although, as discussed by Gallaire et al.? and also observed by Tchoufag et al. \cite{Tchoufag2015}, a convenient definition of the $\epsilon$ improves the results). {\color{red} These aspects are justified by the pertubative nature of the WNL approach. The description of the limit cycle can be extended to larger $Re$ with the approach presented next.  }
